\vspace{-1em}Guidance, please! Towards a framework for RDF-based constraint languages.

### 2015-07-08 paper/paper 2/dc-2015.tex
related work

In this section, we present current languages for constraint formulation and RDF data validation\footnote{
\emph{SPARQL}: \url{http://www.w3.org/TR/sparql11-query}, 
\emph{SPIN}: \url{http://spinrdf.org},
\emph{Pellet ICV}: \url{http://clarkparsia.com/pellet/icv},
\emph{Stardog ICV}: \url{http://docs.stardog.com/#_validating_constraints},
\emph{ShEx}: \url{http://www.w3.org/Submission/shex-defn},
\emph{ReSh}: \url{http://www.w3.org/Submission/shapes},
\emph{DCMI RDF-AP}: \url{http://dublincore.org/documents/singapore-framework},
\emph{Bibframe}: \url{http://bibframe.org},
\emph{DSP}: \url{http://dublincore.org/documents/dc-dsp},
\emph{RDF Schemarama}: \url{http://swordfish.rdfweb.org/discovery/2001/01/schemarama}
%\emph{Schematron}: \url{http://www.schematron.com},
%\emph{XML Schema}: \url{http://www.w3.org/TR/xmlschema-1},
}.
\emph{SPIN}, \emph{SPARQL}, OWL 2, \emph{ShEx}, \emph{ReSh}, and \emph{DSP} are the six most promising and applied languages.
%
The query language for RDF \emph{SPARQL} is generally seen as the method of choice to validate data according to certain constraints \cite{Fuerber2010}, 
although, it is not ideal for their formulation. 
In contrast, high-level constraint languages are comparatively easy to understand and constraints can be formulated more concisely.
Declarative languages may be placed on top of \emph{SPARQL} and \emph{SPIN} when using them as implementation languages.
%
\emph{SPIN} provides a vocabulary to represent \emph{SPARQL} queries as RDF triples
and uses \emph{SPARQL} to specify logical constraints and inference rules \cite{Fuerber2010}.
%
\emph{Stardog ICV} and \emph{Pellet ICV} use OWL 2 constructs to formulate constraints.
The \emph{Pellet Integrity Constraint Validator (ICV)} is a proof-of-concept extension for the \emph{OWL 2 DL} reasoner \emph{Pellet}. 
\emph{Stardog ICV} 
validates RDF data stored in a Stardog database according to 
constraints which may be written in \emph{SPARQL}, \emph{OWL}, or \emph{SWRL}. 
%
\emph{ShEx} specifies a language whose syntax and semantics are similar to regular expressions.
\emph{ShEx} associate RDF graphs with labeled patterns called \emph{shapes} 
which are used to express formal constraints on the content of RDF graphs.
%
\emph{ReSh} defines its own vocabulary for specifying \emph{shapes} of RDF resources.
Ryman et al. define \emph{shape} as a description of the set of triples a resource is expected to contain and of the integrity constraints those triples are required to satisfy \cite{Ryman2013}. 
%
\emph{DCMI RDF Application Profiles (AP)} and \emph{Bibframe} are approaches to specify profiles for application-specific purposes. 
\emph{DCMI RDF-AP} uses \emph{DSP} as generic constraint language which is also intuitive for non-experts.
The \emph{Bibliographic Framework Initiative (Bibframe)} defines a vocabulary which has a strong overlap with \emph{DSP}.
%
Kontokostas et al. define 17 data quality integrity constraints represented as \emph{SPARQL} query templates called \emph{Data Quality Test Patterns (DQTP)} \cite{Kontokostas2014}. 
%
\emph{RDF Schemarama} 
is a proof-of-concept demonstrator based on ideas from \emph{Schematron}. 
It allows to check that RDF data has required properties and
it is based on \emph{Squish}, an SQL-ish query language for RDF, instead of \emph{SPARQL}. 
%
%\emph{Schematron} is an ISO standard for the validation and quality control of XML documents based on XPath and XSLT. 
%
%\emph{XML Schema} is the primary technology for specifying and constraining the structure of XML documents.
%
In addition to the formulation of constraints, \emph{SPIN} (open source API), \emph{Stardog ICV} (as part of the \emph{Stardog RDF database}), \emph{DQTP} (tests), \emph{Pellet ICV} (extension of \emph{Pellet OWL 2 DL} reasoner) and \emph{ShEx} offer executable validation systems using \emph{SPARQL} as implementation language.

>>>>

In this section, we present current languages for RDF constraint formulation and RDF data validation\footnote{
\emph{SPARQL}: \url{http://www.w3.org/TR/sparql11-query}, 
\emph{SPIN}: \url{http://spinrdf.org},
\emph{Pellet ICV}: \url{http://clarkparsia.com/pellet/icv},
\emph{Stardog ICV}: \url{http://docs.stardog.com/#_validating_constraints},
\emph{ShEx}: \url{http://www.w3.org/Submission/shex-defn},
\emph{ReSh}: \url{http://www.w3.org/Submission/shapes},
\emph{DCMI RDF-AP}: \url{http://dublincore.org/documents/singapore-framework},
\emph{Bibframe}: \url{http://bibframe.org},
\emph{DSP}: \url{http://dublincore.org/documents/dc-dsp},
\emph{RDF Schemarama}: \url{http://swordfish.rdfweb.org/discovery/2001/01/schemarama}
%\emph{Schematron}: \url{http://www.schematron.com},
%\emph{XML Schema}: \url{http://www.w3.org/TR/xmlschema-1},
}.
SPIN, SPARQL, OWL 2, ShEx, ReSh, and DSP are the six most promising and mostly used constraint languages.

The \emph{SPARQL Query Language for RDF} \cite{W3C-SPARQL1.1-Query-Language-2013} is generally seen as the method of choice to validate RDF data according to certain constraints \cite{Fuerber2010}, 
although, it is not ideal for their formulation. 
In contrast, high-level constraint languages are comparatively easy to understand and constraints can be formulated more concisely.
Declarative languages may be placed on top of SPARQL and SPIN when using them as implementation languages.
%
The \emph{SPARQL Inferencing Notation (SPIN)} \cite{W3C-SPIN-2011} provides a vocabulary to represent SPARQL queries as RDF triples
and uses SPARQL to specify logical constraints and inference rules \cite{Fuerber2010}.

\emph{Stardog ICV} and \emph{Pellet ICV} use OWL 2 constructs to formulate constraints. The \emph{Pellet Integrity Constraint Validator (ICV)} is a proof-of-concept extension for the \emph{OWL 2 DL} reasoner \emph{Pellet}. \emph{Stardog ICV} validates RDF data stored in a Stardog database according to constraints which may be written in SPARQL, OWL, or SWRL.

\emph{ShEx} specifies a language whose syntax and semantics are similar to regular expressions.
\emph{ShEx} associate RDF graphs with labeled patterns called \emph{shapes} 
which are used to express formal constraints on the content of RDF graphs.

\emph{ReSh} defines its own vocabulary for specifying \emph{shapes} of RDF resources.
Ryman et al. define \emph{shape} as a description of the set of triples a resource is expected to contain and of the integrity constraints those triples are required to satisfy \cite{Ryman2013}.

\emph{DCMI RDF Application Profiles (AP)} and \emph{Bibframe} are approaches to specify profiles for application-specific purposes. 
\emph{DCMI RDF-AP} uses \emph{DSP} as generic constraint language which is also intuitive for non-experts.
The \emph{Bibliographic Framework Initiative (Bibframe)} defines a vocabulary which has a strong overlap with \emph{DSP}.

Kontokostas et al. define 17 data quality integrity constraints represented as \emph{SPARQL} query templates called \emph{Data Quality Test Patterns (DQTP)} \cite{Kontokostas2014}.

\emph{RDF Schemarama} 
is a proof-of-concept demonstrator based on ideas from \emph{Schematron}. 
It allows to check that RDF data has required properties and
it is based on \emph{Squish}, an SQL-ish query language for RDF, instead of \emph{SPARQL}. 
%
%\emph{Schematron} is an ISO standard for the validation and quality control of XML documents based on XPath and XSLT. 
%
%\emph{XML Schema} is the primary technology for specifying and constraining the structure of XML documents.

In addition to the formulation of constraints, \emph{SPIN} (open source API), \emph{Stardog ICV} (as part of the \emph{Stardog RDF database}), \emph{DQTP} (tests), \emph{Pellet ICV} (extension of \emph{Pellet OWL 2 DL} reasoner) and \emph{ShEx} offer executable validation systems using \emph{SPARQL} as implementation language.
